A Middleware for Symmetric Peer-to-Peer Applications

### 2023-03-10 tpds-23/tpds-23.tex
...

\begin{comment}
Os autores mencionam que em cenário com latência de 50ms e 25 eventos por
minuto, os pares precisaram retroceder 3\% do tempo.
Eles devem deixar claro porque isso é uma vantagem e qual a média de período de
tempo aceitável para retrocesso.

- O design experimental precisa ser melhor descrito.
Apenas o emulador das latências é descrito (NetEm).
Como foi realizada (ou qual ferramenta foi usada) a simulação dos experimentos?

- Apenas aplicações com deadline mais curtos adequam-se melhor ao middleware.
Os autores precisam explicar no texto os resultados dos experimentos com maior
latência também (100ms, 250ms e 500ms).
\end{comment}

@@

We perform simulations with over 20 peers in a 5-hop mixed topology with cycles
and straight lines.
We vary the network latency and peer churn, as well as the frequency and
deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the recoverability from churns, such that they validate our
goals above, respectively.
%
As results, we show that goals (b) and (c) are met even under extreme
conditions: peers exhibit a time mismatch of under $0.2\%$ and take less than
$1.5s$ to recover from churns.
%
For the goal (a), we analyze the scenarios in which the middleware can meet
event deadlines with the desired performance.
As an example, peers need to roll back only $3\%$ of the time under a network
latency of $50ms$ and 25 events per minute.

@@

{\footnotesize
~
\begin{verbatim}
enum {
    P2P_EVT_KEY = P2P_EVT_NEXT // key is next to predefs
};
\end{verbatim}
~
}

@@

We run the application main loop at $50~FPS$ ($20ms$ per frame) and calculate
the middleware overhead at each iteration.
We found a negligible overhead of $9us$ in the average, which corresponds to
less than $1/2000$ of the CPU time.
%
In order to have an absolute clock, we use a single machine to simulate all
peers, allowing us to merge their logs into a single file with a comparable
shared timeline.
%
We use \emph{NetEm}~\cite{netem} to simulate the network latency with a normal
distribution.
% (e.g., \code{tc qdisc add dev lo root netem delay 200ms 40ms distribution normal}).
%
We vary
    (i)   the network latency ($5-500ms$ between each peer),
    (ii)  the rate of events ($5-200~evt/sec$), and
    (iii) the deadline $\Delta$ multiplier ($1-5x$).
%
Figure~\ref{fig.mult} shows the $\Delta$s considering the network latency and
chosen multiplier.
For instance, a $50ms$ latency with a $2x$ multiplier results in
$\Delta=500ms$, i.e., each event is triggered with this deadline delay to
compensate the given latency and fixed average of 5 hops
($5 \times 50 \times 2 = 500$).

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{baks}
  \caption{
    \label{fig.baks}
The $5x$, $2x$, and $x$ $\Delta$ regions each contains $36$ measures for
multiple configurations of network latencies ($5-500ms$) and event rates
($5-200~evt/min$).
%
The color thresholds (\emph{white}, \emph{yellow}, \emph{red}, \emph{black})
are arbitrary but help to distinguish between regions of interest.
%
The experiments uses $1$ process for each peer in a single Linux machine
(\emph{Ubuntu 21.04, i7/16GB}).
    }
\end{figure*}

@@

Considering goal (a), we need to take a closer look at Figure~\ref{fig.baks}.
The color patterns indicate clear boundaries for the scenarios that can meet
event deadlines with the desired performance.
%
For instance, high event deadlines (column $5x$) make all scenarios viable,
even with high latencies and event frequencies.
As an application example, chats are not affected by higher event deadlines.
Nevertheless, the higher is the deadline, the less applications suit the
middleware.
%
For the lowest possible $\Delta$ (column $1x$), we see that the middleware can
either handle low latencies with high event frequencies (e.g., $5ms$ with
$100evt/min$) or high lantencies with low event frequencies (e.g., $100ms$ with
$5evt/min$).
%
In summary, the color patterns in the table provide the necessary information
to confront an application with its feasibility or desired performance.

>>>>

@@

We perform simulations with over 20 peers in a 5-hop mixed topology with cycles
and straight lines.
We vary the network latency and peer churn, as well as the frequency and
deadlines of events.
%
We then measure (a) the recurrence of time travels, (b) the real-time pace of
peers, and (c) the recoverability from churns, such that they validate our
goals above, respectively.
%
As results, we show that goals (b) and (c) are met even under extreme
conditions: peers exhibit a time mismatch of under $0.2\%$ and take less than
$1.5s$ to recover from churns.
%
For the goal (a), we analyze the scenarios in which the middleware can meet
event deadlines with the desired performance.
As an example, peers need to roll back only $3\%$ of the time under a network
latency of $50ms$ and 25 events per minute.
%
We consider this overhead negligible for soft real-time applications that do
not depend on instantaneous network feedback, such as chats, watch parties, and
turn-based games.

@@

{\footnotesize
~
\begin{verbatim}
enum {
    P2P_EVT_KEY = P2P_EVT_NEXT // KEY after predefs
};
\end{verbatim}
~
}

@@

\begin{comment}
- O design experimental precisa ser melhor descrito.
Apenas o emulador das latências é descrito (NetEm).
Como foi realizada (ou qual ferramenta foi usada) a simulação dos experimentos?
\end{comment}

We run the application main loop at 50 FPS ($20ms$ per frame) and calculate
the middleware overhead at each iteration.
We found a negligible overhead of $9us$ in the average, which corresponds to
less than $1/2000$ of the CPU time.
%
In order to have an absolute clock, we use a single machine to simulate all
peers, allowing us to merge their logs into a single file with a comparable
shared timeline.
%
We use \emph{NetEm}~\cite{netem} to simulate the network latency with a normal
distribution.
% (e.g., \code{tc qdisc add dev lo root netem delay 200ms 40ms distribution normal}).
%
We vary
    (i)   the network latency ($5-500ms$ between each peer),
    (ii)  the rate of events ($5-200~evt/sec$), and
    (iii) the deadline $\Delta$ multiplier ($1-5x$).
%
Figure~\ref{fig.mult} shows the $\Delta$s considering the network latency and
chosen multiplier.
For instance, a $50ms$ latency with a $2x$ multiplier results in
$\Delta=500ms$, i.e., each event is triggered with this deadline delay to
compensate the given latency and fixed average of 5 hops
($5 \times 50 \times 2 = 500$).

@@

\begin{figure*}
  \centering
  \includegraphics[width=\linewidth]{baks}
  \caption{
    \label{fig.baks}
The squares show the percentage of time travels.
%
The $5x$, $2x$, and $x$ $\Delta$ regions each contains $36$ measures for
multiple configurations of network latencies ($5-500ms$) and event rates
($5-200~evt/min$).
%
The color thresholds (\emph{white}, \emph{yellow}, \emph{red}, \emph{black})
are arbitrary but help to distinguish between regions of interest.
%
The experiments uses $1$ process for each peer in a single Linux machine
(\emph{Ubuntu 21.04, i7/16GB}).
    }
\end{figure*}

@@

Considering goal (a), we need to take a closer look at Figure~\ref{fig.baks}.
The color patterns indicate clear boundaries for the scenarios that can meet
event deadlines with the desired performance.
%
For instance, high event deadlines (column $5x$) make all scenarios viable,
even with high latencies and event frequencies.
As an application example, chats are not affected by higher event deadlines.
Nevertheless, the lower is the deadline, the less applications suit the
middleware.
%
For the lowest possible $\Delta$ (column $1x$), we see that the middleware can
either handle low latencies with high event frequencies (e.g., $5ms$ with
$100evt/min$) or high latencies with low event frequencies (e.g., $100ms$ with
$5evt/min$).
%
The middleware does not perform well under higher network latencies (e.g., over
$250ms$).
This is expected since peers that are multiple hops away take too long to
synchronize past events and may generate future events in the meantime, which
causes time travels.
%
In summary, the color patterns in the table provide the necessary information
to confront an application with its feasibility or desired performance.
